Playing Games: A Case Study in Active Learning Applied to Game Theory

### 2015-06-29 paper/paper.tex
Starting to write section about repeated games.

This activity is still quite passive in terms of physical activity (participants are
seated throughout). Nevertheless it allows the data used for the discussion of
the theory to come directly from the participants.

@@

>>>>

This activity is still quite passive in terms of physical activity (participants are
seated throughout). Nevertheless it allows the data used for the discussion of
the theory to come directly from the participants and further more all students
are active participants and there are no difficulties with regards to
encouraging participation (references to these are discussed in \cite{Rocca2010}).

@@

This activity is used to introduce students to the concepts of repeated games
